---
title: "Case Study"
output: github_document
---

```{r, message= FALSE}
library(tidyverse)
library(p8105.datasets)
data("nyc_airbnb")
```

Most popular and most expensive neighborhood?
Which neighborhood has highest reviews?
Availability related to price?
Room type related to neighborhood?
Is length stya related to neighborhood group?

```{r}
nyc_airbnb =
  nyc_airbnb %>%
  mutate(stars = review_scores_location / 2) %>%
  rename(borough = neighbourhood_group)
```

Try to count things:

```{r}
nyc_airbnb %>%
  janitor::tabyl(borough, room_type) %>%
  pivot_wider(
    names_from = room_type,
    values_from = n
  )
```

Is price correlated with review score?

```{r}
nyc_airbnb %>%
  ggplot(aes(x = price, y = stars)) + geom_point() +
  facet_grid(. ~ room_type)
```

Which neighborhood has highest reviews?

```{r}
nyc_airbnb %>%
  janitor::tabyl(borough, stars)
```

Length of stay vs price

```{r}
nyc_airbnb %>%
  ggplot(aes(x = price, y = minimum_nights, color = borough)) + geom_point(alpha = 0.3)
```

Price and room type

```{r}
nyc_airbnb %>%
  ggplot(aes(x = stars, y = minimum_nights, color = borough)) + geom_point(alpha = 0.3)
```

Price and neighborhood

```{r}
nyc_airbnb %>%
  filter(borough == "Manhattan",
         price <= 1000) %>%
  group_by(neighbourhood) %>%
  summarise(mean_price = mean(price, na.rm = TRUE))

nyc_airbnb %>%
  filter(borough == "Manhattan",
         price <= 1000) %>%
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>%
  ggplot(aes(x = neighbourhood, y = price)) + 
  geom_boxplot() +
  coord_flip() +
  facet_grid(. ~ room_type)
```

Price vs location

```{r}
nyc_airbnb %>%
  filter(price < 500) %>%
  sample_n(5000) %>%
  ggplot(aes(x = lat, y = long, color = price)) + geom_point(alpha = 0.3) 
```


```{r, eval = FALSE}
nyc_airbnb %>%
  filter(price < 500) %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(~lat, ~long)
```


```{r}

```